Empirical Evaluation of eval in R

### 2020-08-28 inst/analysis/analysis_stable.Rmd

library(tidyverse)
library(stringr)
library(viridis)
library(vctrs)
library(DT)
library(fst)
library(fs)
library(ggthemes)

@@

```{r env_assign}
eval_calls_env_assign <- eval_calls %>% filter(!is.na(expr_resolved)) %>% mutate(env_assign = pblapply(expr_resolved, is_assign_str, cl = parallel::detectCores() - 2))
```

@@

>>>>

library(tidyverse)
library(stringr)
library(viridis)
library(vctrs)
library(DT)
library(fst)
library(fs)
library(ggthemes)
library(pbapply)

@@

```{r env_assign}
eval_calls_env_assign <- eval_calls %>% filter(!is.na(expr_resolved)) %>% mutate(env_assign = pblapply(expr_resolved, is_assign_str, cl = parallel::detectCores() - 2))

#eval_calls_env_assign2 <-  eval_calls_env_assign %>% filter(is.logical(env_assign)) %>% hoist("env_assign", env_assign = 1)
```

@@

Number of eval calls in packages.

```{r call_sites_core}

corpus_files <- read_lines(CORPUS_FILE)
corpus_size <- length(corpus_files)

program_call_sites <- read_fst(PACKAGE_EVALS_FILE) %>% as_tibble() %>%
  filter(package %in% c(corpus_files, CORE_PACKAGES))

in_core <- program_call_sites %>% filter(package %in% CORE_PACKAGES)

nb_in_core <- in_core %>% nrow()

r("nb core eval call sites", nb_in_core)

call_sites_per_package <- program_call_sites %>% count(package, sort = TRUE)

max_call_sites <- max(call_sites_per_package$n)

r("max call site package", max_call_sites)

nb_one_call_site <- call_sites_per_package %>% filter(n == 1) %>% nrow()

r("one call site package", nb_one_call_site)

nb_packages_plus_one <- n_distinct(program_call_sites %>% filter(!package %in% CORE_PACKAGES) %>% select(package))

nb_package_none_eval_call_site <- corpus_size - nb_packages_plus_one

r("no call site packages", nb_package_none_eval_call_site)
```
